Model Comparisons

### 2015-11-20 models/Model_Comparison.Rmd
initial alpha tuning for e10 literal listener semantics with e6 pragmatic judgments

## Tune hyperparams
```{r}
# tune.alhpa()
# ------------
# d        --> data
# alphas   --> range of alphas to test
# type     --> full or partial model
# useprior --> use uniform prior
# usenone  --> use gener None
tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F) {
  # Tune best alphas
  fit = sapply(alphas, FUN=function(n) {
    if (type == "partial") {
      md <- d %>%
        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
    } else {
      md <- d %>%
        do(run.full(., alpha = n, useprior = F, usenone = F))
    }
    # MSE
    return(mean((md$pred - md$listener.p)^2))
  })  
  # get lowest MSE
  best.alpha = which(fit == min(fit))
  return(best.alpha)
}
```

@@

# Model 3 - Full, alpha tuning
# ----------------------------
alphas[6] = tune.alpha(data.full, type = "full")
m3.fit = data.full %>%
  do(run.full(., alpha = alphas[6]))
m3.fit.matched = m3.fit[matched.items, ]
m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
# Check that everything lines up between partial and full
all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)^2, 5))
```

>>>>

## Tune hyperparams
```{r}
# tune.alhpa()
# ------------
# d        --> data
# alphas   --> range of alphas to test
# type     --> full or partial model
# useprior --> use uniform prior
# usenone  --> use gener None
tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F, compare.data=NULL) {
  # Tune best alphas
  fit = sapply(alphas, FUN=function(n) {
    if (type == "partial") {
      md = d %>%
        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
    } else {
      md = d %>%
        do(run.full(., alpha = n, useprior = F, usenone = F))
    }
    # Fit to e6 data
    if (!is.null(compare.data)) {
      matched.items = which((md[, "scale"] != "some_all" &
                               (md[, "degree"] == "hi2" | md[, "degree"] == "hi1")) |
                              (md[, "scale"] == "some_all" &
                                 (md[, "degree"] == "hi1" | md[, "degree"] == "low1")))
      md = md[matched.items, ]
      md$degree = ifelse(md$degree == "hi1", "hi", "low")
      stopifnot("listener.p" %in% colnames(compare.data))
      md$listener.p = compare.data$listener.p
    }

    # MSE
    return(mean((md$pred - md$listener.p)^2))
  })  
  # get lowest MSE
  best.alpha = which(fit == min(fit))
  return(best.alpha)
}
```

@@

# Model 3 - Full, alpha tuning
# ----------------------------
alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial)
m3.fit = data.full %>%
  do(run.full(., alpha = alphas[6]))
m3.fit.matched = m3.fit[matched.items, ]
m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
# Check that everything lines up between partial and full
all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)^2, 5))
```
